Using structural and evolutionary information to detect and correct pyrosequencing errors in non-coding RNAs

### 2013-05-28 JCB/methods_JCB.tex

\subsection{Probabilistic Model}
Let $\Omega$ be an gap-free RNA alignment sequence, $S$ its associated secondary structure, 
then any sequence $s$ has probability proportional to its Boltzmann factor
\begin{align*}
  {B}(s) &= e^\frac{-\PE{s}}{RT}, &&\text{with}&\PE{s}&:=\alpha\cdot\ES(s,S)+(1-\alpha)\cdot\EI(s,S,\Omega),
\end{align*}
where $R$ is the Boltzmann constant, $T$ the temperature in Kelvin, $\ES(s)$ and $\EI(s,S,\Omega)$ 
are the free-energy and isostericity contributions respectively (further described below), and $\alpha\in[0,1]$ is an arbitrary parameter that sets the relative weight for both contributions.

>>>>

\subsection{Probabilistic Model}\label{sec:model}
Let $\Omega$ be an gap-free RNA alignment sequence, $S$ its associated secondary structure, 
then any sequence $s$ has probability proportional to its Boltzmann factor
\begin{align*}
  {B}(s) &= e^\frac{-\PE{s}}{RT}, &&\text{with}&\PE{s}&:=\alpha\cdot\ES(s,S)+(1-\alpha)\cdot\EI(s,S,\Omega),
\end{align*}
where $R$ is the Boltzmann constant, $T$ the temperature in Kelvin, $\ES(s)$ and $\EI(s,S,\Omega)$ 
are the free-energy and isostericity contributions respectively (further described below), and $\alpha\in[0,1]$ is an arbitrary parameter that sets the relative weight for both contributions.
